Borders and Gateways: Measuring and Analyzing National AS Chokepoints

### 2018-07-30 Paper/conclusion.tex
Jed made some minor edits

The DNS infrastructure is another potential graph where chokepoints can be
exploited for censorship and surveillance\~cite{Greschbach2016a} and is at a
higher layer in the network stack than IP routes.  However, we leave analysis of
this graph for future work because it is outside the scope of \toolname{} and
because the countries that rely on DNS as their main form of censorship are
fewer in number and are among the least sophisticated in terms of their
censorship regime.

>>>>

The DNS infrastructure is another potential graph where chokepoints can be
exploited for censorship and surveillance~\cite{Greschbach2016a} and is at a
higher layer in the network stack than IP routes.  However, we leave analysis of
this graph for future work because it is outside the scope of \toolname{} and
because the countries that rely on DNS as their main form of censorship are
fewer in number and are among the least sophisticated in terms of their
censorship regime.

### 2018-07-30 Paper/experiment.tex
Start of results
Jed made some minor edits

\section{Experimental Setup}

@@

To probe these questions we first used our chokepoint evaluation technique to
investigate the chokepoint potential of all nations for the current Internet as
well as the change in chokepoint potentials over time. We looked at multiple
snapshots of AS relationships from the CAIDA dataset (2012-2018).  For each
timestamp, we generated routing trees based on these relationships. Then we
calculated the chokepoint potential for every border AS per snapshot using
toolname{}. As a result we can investigate how countries have changed overtime
in their capability to enact censorship and surveillance. This is an attempt to
understand what topological trends have developed historically.  With this test
we can compare nations, and see which ones have overtime increased their
capability to control the flow of information across their borders.

>>>>

\section{Experimental Setup}
\label{sec:exp}

@@

To probe these questions we first used our chokepoint evaluation technique to
investigate the chokepoint potential of all nations for the current Internet as
well as the change in chokepoint potentials over time. We looked at multiple
snapshots of AS relationships from the CAIDA dataset (2012-2018).  For each
timestamp, we generated routing trees based on these relationships. Then we
calculated the chokepoint potential for every border AS per snapshot using
toolname{}. As a result we can investigate how countries have changed over time
in their capability to enact censorship and surveillance. This is an attempt to
understand what topological trends have developed historically.  With this test
we can compare nations, and see which ones have, over time, increased their
capability to control the flow of information across their borders.
